---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
First we will read in the data by making the path of the csv file an object.
```{r}
data <- "C:/Users/SteveC13/Desktop/Data Science Text Books/Reproducible Research/activity.csv"
```
Next we will define what class the columns are to call into the read.csv function.  Using the read.csv function we can call in the data from the csv as a usable data frame.
```{r}
class = c("integer", "character", "integer")
activity <- read.csv(data, head=TRUE, colClasses=class, na.strings="NA")
```
Lasly we will convert the dates to a proper format and also omit any rows that contain an NA from the data frame.
```{r}
activity$date <- as.Date(activity$date)

activity_omitNA <- na.omit(activity)
```

## What is mean total number of steps taken per day?





## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
