---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
First we will read in the data by making the path of the csv file an object.
```{r}
data <- "C:/Users/SteveC13/Desktop/Data Science Text Books/Reproducible Research/activity.csv"
```
Next we will define what class the columns are to call into the read.csv function.  Using the read.csv function we can call in the data from the csv as a usable data frame.
```{r}
class = c("integer", "character", "integer")
activity <- read.csv(data, head=TRUE, colClasses=class, na.strings="NA")
```
Lasly we will convert the dates to a proper format and also omit any rows that contain an NA from the data frame.
```{r}
activity$date <- as.Date(activity$date)

activity_omitNA <- na.omit(activity)
```

## What is mean total number of steps taken per day?
```{r}
library(ggplot2)
library(plyr)

Sumsteps <- aggregate(activity_omitNA$steps~activity_omitNA$date, FUN = sum)
colnames(Sumsteps)<- c("Day", "Number of Steps")
```
Plotting the frequency of steps taken per day
```{r}
hist(Sumsteps$`Number of Steps`, breaks = 10, 
    xlab = "Total Steps", 
    ylab = "Frequency", 
    main = "Frequency of Total Steps Taken Per Day", 
    col = "red")
```
The Mean and Median Steps Taken per Day:
```{r}
mean(Sumsteps$`Number of Steps`)
median(Sumsteps$`Number of Steps`)
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
